Utilizing Design Principles from Glass Sponges for Structurally Robust Lattices

### 2018-10-03 Paper-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.
Updates from ShareLaTeX

\newcommand{\mf}[1]{\colorbox{blue!10}{\color{color3}#1}}

@@

@@

In modern day structural engineering, we find many

The design of diagonal reinforcement for truss systems found in bridges, buildings, and beam structures has not changed much since the introduction of the Long truss design patented by Colonel Long in 1830 \citep{waddell1916}. In modern day structures, we see many different iterations of new truss designs with various applications in mind but with what is the same fundamentally simple diagonal reinforcement technique. This technique, involving two diagonal trusses (one in each direction) crossing the opening of a square beam cell, limits the transverse motion of the main support beams ultimately giving the structure shear capacity and strength. Alternative, methods to strengthen beam structures have been introduced via material \hl{[...],} \mf{needs more information and citations}. However, in this study we seek to further strengthen square lattices through inspiration from a particular sponge species called \textit{Euplectella Aspergillum}, commonly known as the Venus' flower basket. This particular species, which is part of the \textit{Hexactinellid} class, is primarily made of silica and exhibit a periodic and regular grid structure with an intrinsic and different diagonal reinforcement scheme.

@@

 Bibliography
\nocite{*}
\bibliography{refs}
\bibliographystyle{apalike}

>>>>

\newcommand{\mf}[1]{\colorbox{blue!10}{\color{color3}#1}}
\newcommand{\KB}[1]{\noindent\color{blue}$\Longrightarrow$ #1\normalcolor}

@@

\begin{figure*}[ht]
	\captionsetup{width=0.8\textwidth}
	\begin{center}
		\includegraphics[width=0.7\textwidth]{Fig4}
	\end{center}
	\caption{\textbf{text} Figure showing (a) (b)} \label{Fig4}
\end{figure*}

@@

\KB{Lattice structures with well-defined periodicity are ubiquitous
 in synthetic structures and
devices as they offer novel and unique
properties, including light weight REFs,  high energy absorption REFs,
 and the ability to control the propagation of both
electromagnetic REFs and elastic waves REFs and heat flow REFs.} \KB{INTRODUCE THE SQUARE LATTICE AN SAY THAT IT IS VERY POPULAR BUT UNSTABLE. NEED FOR REINFORCEMENT}

The design of diagonal reinorcement for truss systems found in bridges, buildings, and beam structures has not changed much since the introduction of the Long truss design patented by Colonel Long in 1830 \citep{waddell1916}. In modern day structures, we see many different iterations of new truss designs with various applications in mind but with what is the same fundamentally simple diagonal reinforcement technique. This technique, involving two diagonal trusses (one in each direction) crossing the opening of a square beam cell, limits the transverse motion of the main support beams ultimately giving the structure shear capacity and strength. Alternative, methods to strengthen beam structures have been introduced via material \hl{[...],} \mf{needs more information and citations}. However, in this study we seek to further strengthen square lattices through inspiration from a particular sponge species called \textit{Euplectella Aspergillum}, commonly known as the Venus' flower basket. This particular species, which is part of the \textit{Hexactinellid} class, is primarily made of silica and exhibit a periodic and regular grid structure with an intrinsic and different diagonal reinforcement scheme.

@@

\nocite{*}
\bibliography{refs}
\bibliographystyle{apalike}
